\Large{Holier Than Thou: Partisan Gap in Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}

### 2022-12-21 ms/adult.tex
Add difference in medians
Add difference in medians for porn consumption by party. Currently Table SI 1.7.

%==============================================================================
% Table for balance of porn consumption and individual characteristics by party
%==============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
	\caption{Differences in Porn Consumption and Individual Characteristics by Party}
	\label{tab:characteristics_split_by_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
			\toprule
			&\multicolumn{7}{c}{\underline{Panel A. Measures of porn consumption}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_outcomes_by_party.tex}\\
			%-------------------------------------------------------------------
			\cmidrule{2-8}
			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_covariates_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\scriptsize \emph{Notes:}
		Table shows splits by party for porn consumption and for individual characteristics for the 1,200 individuals.
		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
		Column (1) shows subgroups for categorical variables.
		Column (2) indicates the count of missing variables, if any.
		Columns (3)--(5) show mean and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, Democratic individuals, and Republican individuals.
		Standard deviations and percentages in parentheses.
		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
	}
\end{table}

%==============================================================================
% Table for balance of porn consumption and individual characteristics by party
%==============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
	\caption{Differences in Porn Consumption and Individual Characteristics by Porn Consumers}
	\label{tab:characteristics_split_by_porn_consumers}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
			\toprule
			&\multicolumn{7}{c}{\underline{Panel A. Measures of porn consumption}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_outcomes_by_porn_consumers.tex}\\
			%-------------------------------------------------------------------
			\cmidrule{2-8}
			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_covariates_by_porn_consumers.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\scriptsize \emph{Notes:}
		Table shows splits by consumers of porn for porn consumption and for individual characteristics for the 1,200 individuals.
		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
		Column (1) shows subgroups for categorical variables.
		Column (2) indicates the count of missing variables, if any.
		Columns (3)--(5) show mean and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, non-consumers of porn, and consumers of porn.
		Standard deviations and percentages in parentheses.
		Column (6) and column (7) report the p-values and standardized mean differences for non-consumers vs consumers.
	}
\end{table}

>>>>

%==============================================================================
% Table for balance of porn consumption and individual characteristics by party
%==============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
	\caption{Differences in Porn Consumption and Individual Characteristics by Party}
	\label{tab:characteristics_split_by_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
			\toprule
			&\multicolumn{7}{c}{\underline{Panel A. Measures of porn consumption}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_outcomes_by_party.tex}\\
			%-------------------------------------------------------------------
			\cmidrule{2-8}
			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_covariates_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\scriptsize \emph{Notes:}
		Table shows splits by party for porn consumption and for individual characteristics for the 1,200 individuals.
		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
		Column (1) shows subgroups for categorical variables.
		Column (2) indicates the count of missing variables, if any.
		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, Democratic individuals, and Republican individuals.
		Standard deviations and percentages in parentheses.
		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
		Given the skew in porn consumption, we also performed tests for difference in means medians for the measures of porn consumption by party. See \cref{tab:characteristics_split_by_party_medians}.
	}
\end{table}

%==============================================================================
% Table for balance of porn consumption and individual characteristics by party
%==============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
	\caption{Differences in Porn Consumption and Individual Characteristics by Porn Consumers}
	\label{tab:characteristics_split_by_porn_consumers}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
			\toprule
			&\multicolumn{7}{c}{\underline{Panel A. Measures of porn consumption}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_outcomes_by_porn_consumers.tex}\\
			%-------------------------------------------------------------------
			\cmidrule{2-8}
			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_covariates_by_porn_consumers.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\scriptsize \emph{Notes:}
		Table shows splits by consumers of porn for porn consumption and for individual characteristics for the 1,200 individuals.
		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
		Column (1) shows subgroups for categorical variables.
		Column (2) indicates the count of missing variables, if any.
		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, non-consumers of porn, and consumers of porn.
		Standard deviations and percentages in parentheses.
		Column (6) and column (7) report the p-values and standardized mean differences for non-consumers vs consumers.
	}
\end{table}

%==============================================================================
% Table for balance of porn consumption and individual characteristics by party
% Difference in medians
%==============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
	\caption{Differences (in Medians) in Porn Consumption and Individual Characteristics by Party}
	\label{tab:characteristics_split_by_party_medians}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
			\toprule
			&\multicolumn{7}{c}{\underline{Measures of porn consumption}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrats}&\multicolumn{1}{c}{Republicans}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_outcomes_by_party_medians.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\scriptsize \emph{Notes:}
		Table shows splits by party for porn consumption and for individual characteristics for the 1,200 individuals.
		This table focuses on differences in medians.
		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
		Column (1) shows subgroups for categorical variables.
		Column (2) indicates the count of missing variables, if any.
		Columns (3)--(5) show the medians, the first quartiles, and the third quartiles, for the full sample, Democrats, and Republicans.
		Standard deviations and percentages in parentheses.
		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
	}
\end{table}
